|

### 2018-11-02 paper.Rmd
A few small changes.

Table \@ref(tab-summarystats) shows summary stats of your data. I normally use `stargazer()` [@hlavac2013stargazer] which offers extreme flexibility regarding table output (see `?stargazer`).

```{r echo=TRUE, message=FALSE, warning=FALSE, paged.print=FALSE, results="asis"}
library(stargazer)
stargazer(cars, 
          title = "Summary table with stargazer",
          label="tab-summarystats", 
          table.placement = "H", 
          header=FALSE)
```

Table \@ref(tab-regression) shows the output for a regression table. Make sure you name all your models and explicitly refer to model names (M1, M2 etc.) in the text.

```{r echo=TRUE, message=FALSE, warning=FALSE, paged.print=FALSE, results="asis"}
library(stargazer)
model1 <- lm(speed ~ dist, data = cars)
model2 <- lm(speed ~ dist, data = cars)
model3 <- lm(dist ~ speed, data = cars)
stargazer(model1, model2, model3,
          title = "Regression table with stargazer",
          label="tab-regression", 
          table.placement = "H", 
          column.labels = c("M1", "M2", "M3"),
          model.numbers = FALSE,
          header=FALSE)
```

@@

Another great function is `kable()` (`knitr` package) in combination with `kableExtra`. Table \@ref(tab:tab-kabletable) provides an example. Again you can modify so many things in both the `kable()` and the `kable_styling()` function. See [this overview](https://haozhu233.github.io/kableExtra/awesome_table_in_pdf.pdf) of all the kable stylings that are possible provided by the package author himself.

```{r tab-kabletable, echo=TRUE, message=FALSE, warning=FALSE, paged.print=FALSE, results="asis"}
library(knitr)
library(kableExtra)
kable(cars[1:10,], row.names = TRUE, caption = 'Table with kable() and kablestyling()', 
      format = "latex", booktabs = T) %>%
        kable_styling(full_width = T, 
                      latex_options = c("striped", 
                                        "scale_down",
                                        "HOLD_position"),
                      font_size = 10)
```

>>>>

Table \@ref(tab1) shows summary stats of your data.^[To reference the table where you set the identifier in the stargazer function you only need to use the actual label, i.e., ´tab1´.] I normally use `stargazer()` [@hlavac2013stargazer] which offers extreme flexibility regarding table output (see `?stargazer`).

```{r echo=TRUE, message=FALSE, warning=FALSE, paged.print=FALSE, results="asis"}
library(stargazer)
stargazer(cars, 
          title = "Summary table with stargazer",
          label="tab1", 
          table.placement = "H", 
          header=FALSE)
```

Table \@ref(tab2) shows the output for a regression table. Make sure you name all your models and explicitly refer to model names (M1, M2 etc.) in the text.

```{r echo=TRUE, message=FALSE, warning=FALSE, paged.print=FALSE, results="asis"}
library(stargazer)
model1 <- lm(speed ~ dist, data = cars)
model2 <- lm(speed ~ dist, data = cars)
model3 <- lm(dist ~ speed, data = cars)
stargazer(model1, model2, model3,
          title = "Regression table with stargazer",
          label="tab2", 
          table.placement = "H", 
          column.labels = c("M1", "M2", "M3"),
          model.numbers = FALSE,
          header=FALSE)
```

@@

Another great function is `kable()` (`knitr` package) in combination with `kableExtra`. Table \@ref(tab:tab3) provides an example.^[To reference the table produced by the chunk you need to add ´tab:´ to the chunk name, i.e., ´tab:tab3´.] Again you can modify so many things in both the `kable()` and the `kable_styling()` function. See [this overview](https://haozhu233.github.io/kableExtra/awesome_table_in_pdf.pdf) of all the kable stylings that are possible provided by the package author himself.

```{r tab3, echo=TRUE, message=FALSE, warning=FALSE, paged.print=FALSE, results="asis"}
library(knitr)
library(kableExtra)
kable(cars[1:10,], row.names = TRUE, 
      caption = 'Table with kable() and kablestyling()', 
      format = "latex", booktabs = T) %>%
        kable_styling(full_width = T, 
                      latex_options = c("striped", 
                                        "scale_down",
                                        "HOLD_position"),
                      font_size = 10)
```

### 2018-11-02 paper.tex
A few small changes.

\begin{itemize}
\tightlist
\item
  \textbf{Access}: Research is normally funded by taxpayers (researchers
  are also taxpayers). Hence, it should be freely accessible to everyone
  without any barriers, e.g., without requiring commercial software.
  Importantly, researchers from developing countries are even more
  dependent on free access to knowledge (Kirsop and Chan
  \protect\hyperlink{ref-Kirsop2005-ro}{2005}).
\item
  \textbf{Reproducability}: Even if you have written a study and
  analyzed the data yourself you will forget what you did after a few
  months. A fully reproducable setup will help you to trace back your
  own steps. Obviously, the same is true for other researchers who may
  want to understand your work and built on it. It may sound like a joke
  but why not aim for reproducability in 500 years.
\item
  \textbf{Errors}: Manual steps in data analysis (e.g., manually
  copy/pasting values into a table etc.) may introduce errors. R
  Markdown allows you to \textbf{automatize} such steps and/or avoid
  them.
\item
  \textbf{Revisions}: Revising a paper takes much less time, if you have
  all the code you need in one place, i.e., one \texttt{.rmd} file. For
  instance, if you decide to exclude a subset of your data you simply
  need to insert one line of your code at the beginning and everything
  is rebuilt/re-estimated automatically.
\end{itemize}

@@

Table \ref{tab-summarystats} shows summary stats of your data. I
normally use \texttt{stargazer()} (Hlavac
\protect\hyperlink{ref-hlavac2013stargazer}{2013}) which offers extreme
flexibility regarding table output (see \texttt{?stargazer}).

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{library}\NormalTok{(stargazer)}
\KeywordTok{stargazer}\NormalTok{(cars, }
          \DataTypeTok{title =} \StringTok{"Summary table with stargazer"}\NormalTok{,}
          \DataTypeTok{label=}\StringTok{"tab-summarystats"}\NormalTok{, }
          \DataTypeTok{table.placement =} \StringTok{"H"}\NormalTok{, }
          \DataTypeTok{header=}\OtherTok{FALSE}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{table}[H] \centering 
  \caption{Summary table with stargazer} 
  \label{tab-summarystats} 
\begin{tabular}{@{\extracolsep{5pt}}lccccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
Statistic & \multicolumn{1}{c}{N} & \multicolumn{1}{c}{Mean} & \multicolumn{1}{c}{St. Dev.} & \multicolumn{1}{c}{Min} & \multicolumn{1}{c}{Pctl(25)} & \multicolumn{1}{c}{Pctl(75)} & \multicolumn{1}{c}{Max} \\ 
\hline \\[-1.8ex] 
speed & 50 & 15.400 & 5.288 & 4 & 12 & 19 & 25 \\ 
dist & 50 & 42.980 & 25.769 & 2 & 26 & 56 & 120 \\ 
\hline \\[-1.8ex] 
\end{tabular} 
\end{table}

Table \ref{tab-regression} shows the output for a regression table. Make
sure you name all your models and explicitly refer to model names (M1,
M2 etc.) in the text.

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{library}\NormalTok{(stargazer)}
\NormalTok{model1 <-}\StringTok{ }\KeywordTok{lm}\NormalTok{(speed }\OperatorTok{~}\StringTok{ }\NormalTok{dist, }\DataTypeTok{data =}\NormalTok{ cars)}
\NormalTok{model2 <-}\StringTok{ }\KeywordTok{lm}\NormalTok{(speed }\OperatorTok{~}\StringTok{ }\NormalTok{dist, }\DataTypeTok{data =}\NormalTok{ cars)}
\NormalTok{model3 <-}\StringTok{ }\KeywordTok{lm}\NormalTok{(dist }\OperatorTok{~}\StringTok{ }\NormalTok{speed, }\DataTypeTok{data =}\NormalTok{ cars)}
\KeywordTok{stargazer}\NormalTok{(model1, model2, model3,}
          \DataTypeTok{title =} \StringTok{"Regression table with stargazer"}\NormalTok{,}
          \DataTypeTok{label=}\StringTok{"tab-regression"}\NormalTok{, }
          \DataTypeTok{table.placement =} \StringTok{"H"}\NormalTok{, }
          \DataTypeTok{column.labels =} \KeywordTok{c}\NormalTok{(}\StringTok{"M1"}\NormalTok{, }\StringTok{"M2"}\NormalTok{, }\StringTok{"M3"}\NormalTok{),}
          \DataTypeTok{model.numbers =} \OtherTok{FALSE}\NormalTok{,}
          \DataTypeTok{header=}\OtherTok{FALSE}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{table}[H] \centering 
  \caption{Regression table with stargazer} 
  \label{tab-regression} 
\begin{tabular}{@{\extracolsep{5pt}}lccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{3}{c}{\textit{Dependent variable:}} \\ 
\cline{2-4} 
\\[-1.8ex] & \multicolumn{2}{c}{speed} & dist \\ 
 & M1 & M2 & M3 \\ 
\hline \\[-1.8ex] 
 dist & 0.166$^{***}$ & 0.166$^{***}$ &  \\ 
  & (0.017) & (0.017) &  \\ 
  & & & \\ 
 speed &  &  & 3.932$^{***}$ \\ 
  &  &  & (0.416) \\ 
  & & & \\ 
 Constant & 8.284$^{***}$ & 8.284$^{***}$ & $-$17.579$^{**}$ \\ 
  & (0.874) & (0.874) & (6.758) \\ 
  & & & \\ 
\hline \\[-1.8ex] 
Observations & 50 & 50 & 50 \\ 
R$^{2}$ & 0.651 & 0.651 & 0.651 \\ 
Adjusted R$^{2}$ & 0.644 & 0.644 & 0.644 \\ 
Residual Std. Error (df = 48) & 3.156 & 3.156 & 15.380 \\ 
F Statistic (df = 1; 48) & 89.567$^{***}$ & 89.567$^{***}$ & 89.567$^{***}$ \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{3}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table}

@@

Another great function is \texttt{kable()} (\texttt{knitr} package) in
combination with \texttt{kableExtra}. Table \ref{tab:tab-kabletable}
provides an example. Again you can modify so many things in both the
\texttt{kable()} and the \texttt{kable\_styling()} function. See
\href{https://haozhu233.github.io/kableExtra/awesome_table_in_pdf.pdf}{this
overview} of all the kable stylings that are possible provided by the
package author himself.

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{library}\NormalTok{(knitr)}
\KeywordTok{library}\NormalTok{(kableExtra)}
\KeywordTok{kable}\NormalTok{(cars[}\DecValTok{1}\OperatorTok{:}\DecValTok{10}\NormalTok{,], }\DataTypeTok{row.names =} \OtherTok{TRUE}\NormalTok{, }\DataTypeTok{caption =} \StringTok{'Table with kable() and kablestyling()'}\NormalTok{, }
      \DataTypeTok{format =} \StringTok{"latex"}\NormalTok{, }\DataTypeTok{booktabs =}\NormalTok{ T) }\OperatorTok{%>%}
\StringTok{        }\KeywordTok{kable_styling}\NormalTok{(}\DataTypeTok{full_width =}\NormalTok{ T, }
                      \DataTypeTok{latex_options =} \KeywordTok{c}\NormalTok{(}\StringTok{"striped"}\NormalTok{, }
                                        \StringTok{"scale_down"}\NormalTok{,}
                                        \StringTok{"HOLD_position"}\NormalTok{),}
                      \DataTypeTok{font_size =} \DecValTok{10}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

@@

\caption{\label{tab:tab-kabletable}Table with kable() and kablestyling()}
\centering
\resizebox{\linewidth}{!}{
\fontsize{10}{12}\selectfont
\begin{tabu} to \linewidth {>{\raggedright}X>{\raggedleft}X>{\raggedleft}X}
\hiderowcolors
\toprule
  & speed & dist\\
\midrule
\showrowcolors
1 & 4 & 2\\
2 & 4 & 10\\
3 & 7 & 4\\
4 & 7 & 22\\
5 & 8 & 16\\
\addlinespace
6 & 9 & 10\\
7 & 10 & 18\\
8 & 10 & 26\\
9 & 10 & 34\\
10 & 11 & 17\\
\bottomrule
\end{tabu}}
\end{table}

@@

          \DataTypeTok{label=}\StringTok{"tab-summarystats"}\NormalTok{, }

@@

          \DataTypeTok{label=}\StringTok{"tab-regression"}\NormalTok{, }

@@

\KeywordTok{kable}\NormalTok{(cars[}\DecValTok{1}\OperatorTok{:}\DecValTok{10}\NormalTok{,], }\DataTypeTok{row.names =} \OtherTok{TRUE}\NormalTok{, }\DataTypeTok{caption =} \StringTok{'Table with kable() and kablestyling()'}\NormalTok{, }

>>>>

\begin{itemize}
\tightlist
\item
  \textbf{Access}: Research is normally funded by taxpayers (researchers
  are also taxpayers). Hence, it should be freely accessible to everyone
  without any barriers, e.g., without requiring commercial software.
  Importantly, researchers from developing countries are even more
  dependent on free access to knowledge (Kirsop and Chan
  \protect\hyperlink{ref-Kirsop2005-ro}{2005}).
\item
  \textbf{Reproducability}: Even if you have written a study and
  analyzed the data yourself you will forget what you did after a few
  months. A fully reproducable setup will help you to trace back your
  own steps. Obviously, the same is true for other researchers who may
  want to understand your work and built on it. It may sound like a joke
  but why not aim for a document that can be used to reproduce your
  findings in in 500 years.
\item
  \textbf{Errors}: Manual steps in data analysis (e.g., manually
  copy/pasting values into a table etc.) may introduce errors. R
  Markdown allows you to \textbf{automatize} such steps and/or avoid
  them.
\item
  \textbf{Revisions}: Revising a paper takes much less time if you have
  all the code you need in one place, i.e., one \texttt{.rmd} file. For
  instance, if you decide to exclude a subset of your data you simply
  need to insert one line of your code at the beginning and everything
  is rebuilt/re-estimated automatically.
\end{itemize}

@@

Table \ref{tab1} shows summary stats of your data.\footnote{To reference
  the table where you set the identifier in the stargazer function you
  only need to use the actual label, i.e., ´tab1´.} I normally use
\texttt{stargazer()} (Hlavac
\protect\hyperlink{ref-hlavac2013stargazer}{2013}) which offers extreme
flexibility regarding table output (see \texttt{?stargazer}).

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{library}\NormalTok{(stargazer)}
\KeywordTok{stargazer}\NormalTok{(cars, }
          \DataTypeTok{title =} \StringTok{"Summary table with stargazer"}\NormalTok{,}
          \DataTypeTok{label=}\StringTok{"tab1"}\NormalTok{, }
          \DataTypeTok{table.placement =} \StringTok{"H"}\NormalTok{, }
          \DataTypeTok{header=}\OtherTok{FALSE}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{table}[H] \centering 
  \caption{Summary table with stargazer} 
  \label{tab1} 
\begin{tabular}{@{\extracolsep{5pt}}lccccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
Statistic & \multicolumn{1}{c}{N} & \multicolumn{1}{c}{Mean} & \multicolumn{1}{c}{St. Dev.} & \multicolumn{1}{c}{Min} & \multicolumn{1}{c}{Pctl(25)} & \multicolumn{1}{c}{Pctl(75)} & \multicolumn{1}{c}{Max} \\ 
\hline \\[-1.8ex] 
speed & 50 & 15.400 & 5.288 & 4 & 12 & 19 & 25 \\ 
dist & 50 & 42.980 & 25.769 & 2 & 26 & 56 & 120 \\ 
\hline \\[-1.8ex] 
\end{tabular} 
\end{table}

Table \ref{tab2} shows the output for a regression table. Make sure you
name all your models and explicitly refer to model names (M1, M2 etc.)
in the text.

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{library}\NormalTok{(stargazer)}
\NormalTok{model1 <-}\StringTok{ }\KeywordTok{lm}\NormalTok{(speed }\OperatorTok{~}\StringTok{ }\NormalTok{dist, }\DataTypeTok{data =}\NormalTok{ cars)}
\NormalTok{model2 <-}\StringTok{ }\KeywordTok{lm}\NormalTok{(speed }\OperatorTok{~}\StringTok{ }\NormalTok{dist, }\DataTypeTok{data =}\NormalTok{ cars)}
\NormalTok{model3 <-}\StringTok{ }\KeywordTok{lm}\NormalTok{(dist }\OperatorTok{~}\StringTok{ }\NormalTok{speed, }\DataTypeTok{data =}\NormalTok{ cars)}
\KeywordTok{stargazer}\NormalTok{(model1, model2, model3,}
          \DataTypeTok{title =} \StringTok{"Regression table with stargazer"}\NormalTok{,}
          \DataTypeTok{label=}\StringTok{"tab2"}\NormalTok{, }
          \DataTypeTok{table.placement =} \StringTok{"H"}\NormalTok{, }
          \DataTypeTok{column.labels =} \KeywordTok{c}\NormalTok{(}\StringTok{"M1"}\NormalTok{, }\StringTok{"M2"}\NormalTok{, }\StringTok{"M3"}\NormalTok{),}
          \DataTypeTok{model.numbers =} \OtherTok{FALSE}\NormalTok{,}
          \DataTypeTok{header=}\OtherTok{FALSE}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{table}[H] \centering 
  \caption{Regression table with stargazer} 
  \label{tab2} 
\begin{tabular}{@{\extracolsep{5pt}}lccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{3}{c}{\textit{Dependent variable:}} \\ 
\cline{2-4} 
\\[-1.8ex] & \multicolumn{2}{c}{speed} & dist \\ 
 & M1 & M2 & M3 \\ 
\hline \\[-1.8ex] 
 dist & 0.166$^{***}$ & 0.166$^{***}$ &  \\ 
  & (0.017) & (0.017) &  \\ 
  & & & \\ 
 speed &  &  & 3.932$^{***}$ \\ 
  &  &  & (0.416) \\ 
  & & & \\ 
 Constant & 8.284$^{***}$ & 8.284$^{***}$ & $-$17.579$^{**}$ \\ 
  & (0.874) & (0.874) & (6.758) \\ 
  & & & \\ 
\hline \\[-1.8ex] 
Observations & 50 & 50 & 50 \\ 
R$^{2}$ & 0.651 & 0.651 & 0.651 \\ 
Adjusted R$^{2}$ & 0.644 & 0.644 & 0.644 \\ 
Residual Std. Error (df = 48) & 3.156 & 3.156 & 15.380 \\ 
F Statistic (df = 1; 48) & 89.567$^{***}$ & 89.567$^{***}$ & 89.567$^{***}$ \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{3}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table}

@@

Another great function is \texttt{kable()} (\texttt{knitr} package) in
combination with \texttt{kableExtra}. Table \ref{tab:tab3} provides an
example.\footnote{To reference the table produced by the chunk you need
  to add ´tab:´ to the chunk name, i.e., ´tab:tab3´.} Again you can
modify so many things in both the \texttt{kable()} and the
\texttt{kable\_styling()} function. See
\href{https://haozhu233.github.io/kableExtra/awesome_table_in_pdf.pdf}{this
overview} of all the kable stylings that are possible provided by the
package author himself.

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{library}\NormalTok{(knitr)}
\KeywordTok{library}\NormalTok{(kableExtra)}
\KeywordTok{kable}\NormalTok{(cars[}\DecValTok{1}\OperatorTok{:}\DecValTok{10}\NormalTok{,], }\DataTypeTok{row.names =} \OtherTok{TRUE}\NormalTok{, }
      \DataTypeTok{caption =} \StringTok{'Table with kable() and kablestyling()'}\NormalTok{, }
      \DataTypeTok{format =} \StringTok{"latex"}\NormalTok{, }\DataTypeTok{booktabs =}\NormalTok{ T) }\OperatorTok{%>%}
\StringTok{        }\KeywordTok{kable_styling}\NormalTok{(}\DataTypeTok{full_width =}\NormalTok{ T, }
                      \DataTypeTok{latex_options =} \KeywordTok{c}\NormalTok{(}\StringTok{"striped"}\NormalTok{, }
                                        \StringTok{"scale_down"}\NormalTok{,}
                                        \StringTok{"HOLD_position"}\NormalTok{),}
                      \DataTypeTok{font_size =} \DecValTok{10}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

@@

\caption{\label{tab:tab3}Table with kable() and kablestyling()}
\centering
\resizebox{\linewidth}{!}{
\fontsize{10}{12}\selectfont
\begin{tabu} to \linewidth {>{\raggedright}X>{\raggedleft}X>{\raggedleft}X}
\hiderowcolors
\toprule
  & speed & dist\\
\midrule
\showrowcolors
1 & 4 & 2\\
2 & 4 & 10\\
3 & 7 & 4\\
4 & 7 & 22\\
5 & 8 & 16\\
\addlinespace
6 & 9 & 10\\
7 & 10 & 18\\
8 & 10 & 26\\
9 & 10 & 34\\
10 & 11 & 17\\
\bottomrule
\end{tabu}}
\end{table}

@@

          \DataTypeTok{label=}\StringTok{"tab1"}\NormalTok{, }

@@

          \DataTypeTok{label=}\StringTok{"tab2"}\NormalTok{, }

@@

\KeywordTok{kable}\NormalTok{(cars[}\DecValTok{1}\OperatorTok{:}\DecValTok{10}\NormalTok{,], }\DataTypeTok{row.names =} \OtherTok{TRUE}\NormalTok{, }
      \DataTypeTok{caption =} \StringTok{'Table with kable() and kablestyling()'}\NormalTok{, }
